\chapter{Conclusion}

The core that is required to build applications is complete and the library is
already in a usable state. It can read important repository properties and
applications can be scripted in JavaScript to work with the log, index etc. The
project is modular, and new features can be added relatively easily now. The
section 'work done' elaborates on this.

Organizing the entire project and getting started were the difficult challenges.
v8 is a very mature and fast moving project and getting started with it was
quite difficult. Lack of an active, newbie friendly community made it harder.
Libgit2 is relatively a much smaller project and the source and generated
documentation was good enough to understand the concepts.

This project helped to gain a insight into the git, v8 and node ecosystems. All
efforts will be put into stabilizing and completing the necessary features so
that the library is good enough to write 3rd party applications. Even though the
project load was underestimated, most of it could be finished on time and the
project is in a usable state now and can be considered an overall success. The
research on this project was really a good learning experience and will be
continued even after the project duration.

In the next iteration of the project will try to stabilize and test the
asynchronous API properly. Tests and documentation will be improved. Priority
will be given to package the application as a npm library for one line
installation. Testing the system to measure its performance in real world
scenarios will be done if time permits. A GUI application/visualizer using the
library is also planned and will start working on that soon after the major
milestones are complete.
