\section{Git}

Git is fundamentally a content addressable filesystem with a VCS user interface
written on top of it. It is a simple key value data store were you can insert
any kind of content into it, and it will give you back a key - a SHA1 id that
you can use to retrieve the content again at any time.

Git’s design was inspired\cite{inspiration} by BitKeeper and Monotone. It was
originally designed as a low level version control system engine on top of which
others could write front ends. However, the core project has since become a
complete revision control system that is usable directly. More of this will be
discussed later.

\subsection{Characteristics \& Features}

\footnotetext[1]{This section is inspired by the git community book available at
  \url{http://git-scm.com/book}}

Git's\footnotemark[1] design is a synthesis of Torvalds’ experience with Linux
in maintaining a large distributed development project, along with his intimate
knowledge of file system performance gained from the same project and the urgent
need to produce a working system in short order. These influences led to the
following implementation choices:

\begin{description}

\item[1. Strong support for non linear development] \hfill \\
  Git supports rapid branching and merging, and includes specific tools for
  visualizing and navigating a nonlinear development history. Branches in git
  are very lightweight: A branch in git is only a reference to a single commit.
  With its parental commits, the full branch structure can be constructed.

\item[2. Distributed development] \hfill \\
  Like Darcs, BitKeeper, Mercurial, SVK, Bazaar and Monotone, Git gives each
  developer a local copy of the entire development history, and changes are
  copied from one such repository to another. These changes are imported as
  additional development branches, and can be merged in the same way as a
  locally developed branch.

\item[3. Compatibility with existing systems/protocols] \hfill \\
  Repositories can be published via HTTP, FTP, rsync, or a Git protocol over
  either a plain socket or ssh. Git also has a CVS server emulation, which
  enables the use of existing CVS clients and IDE plugins to access Git
  repositories. Subversion and SVK repositories can be used directly with
  git-svn.

\item[4. Efficient handling of large projects] \hfill \\
  Git is very fast and scalable, and performance tests showed it was an order of
  magnitude faster than some revision control systems, and fetching revision
  history from a locally stored repository can be one hundred times faster than
  fetching it from the remote server. In particular, Git does not get slower as
  the project history grows larger.

\item[5. Cryptographic authentication of history] \hfill \\
  The Git history is stored in such a way that the id of a particular revision
  (a commit in Git terms) depends upon the complete development history leading
  up to that commit. Once it is published, it is not possible to change the old
  versions without it being noticed.

\item[6. Toolkit based design] \hfill \\
  Git was designed as a set of programs written in C, and a number of shell and
  perl scripts that provide wrappers around those programs. Although most of
  those scripts have since been rewritten in C for speed and portability, the
  design remains, and it is easy to chain the components together.

\item[7. Garbage accumulates unless collected] \hfill \\
  Aborting operations or backing out changes will leave useless dangling objects
  in the database. These are generally a small fraction of the continuously
  growing history of wanted objects. Git will automatically perform garbage
  collection when enough loose objects have been created in the repository or
  after a specific interval like a month or a week. Garbage collection can be
  called explicitly using ‘git gc –prune‘.

\item[8. Periodic object packing] \hfill \\
  Git stores each newly created object as a separate file. Although individually
  compressed, this takes a great deal of space and is inefficient. This is
  solved by the use of packs that store a large number of objects in a single
  file (or network byte stream) called packfile, delta compressed among
  themselves. Newly created objects (newly added history) are still stored
  singly, and periodic repacking is required to maintain space efficiency.

\end{description}
