\chapter{Introduction}

Git\cite{git} is one of the most popular developer tools in use today and a lot
of very important opensource and closed source programs use it to coordinate
development. Few of the major projects that use git are the \textit{Linux
  kernel}, Perl language, WebKit, Gnome, Apache Foundation, jQuery, Emacs and
git itself! Organizations like Facebook, Google and Microsoft use it internally
to develop their core products.

JavaScript\cite{javascript} the only language available on the biggest computing
platform today - the web browser. It is available on almost all of the modern
devices and is one of the most popular languages in active use today. Years of
development polished the language so well and is very modern and powerful now.

The two tools in question, Git and JavaScript are widely separated. Git was
originally designed to be used from a standard Linux shell and JavaScript
generally executes in the browser.

Its not possible to shell out system commands or write native extensions in C
out of the box for JavaScript and It makes linking both of them together a hard
task. \textit{This project looks into the possibility of making them work
  together}.

\section{Overview}

Git is a free and open source distributed version control system designed to
handle everything from small to very large projects with speed and efficiency.
It was initially designed and developed by Linus Torvalds for Linux kernel
development; it has since been adopted by many other projects.

JavaScript (JS) is an interpreted computer programming language originally
implemented as part of web browsers so that client-side scripts could interact
with the user, control the browser, communicate asynchronously, and alter the
document content that was displayed. It is prototype-based, dynamic, weakly
typed, and has first-class functions. Its syntax was influenced by the language
C. JavaScript copies many names and naming conventions from Java, but the two
languages are otherwise unrelated and have very different semantics. The key
design principles within JavaScript are taken from the Self and Scheme
programming languages. It is a multi-paradigm language, supporting
object-oriented, imperative, and functional programming styles.

Git's primary user interface is the command line shell and it is really good in
its own way. There are alternate user interfaces for git, like
magit\cite{magit}, an interface heavily optimized for Emacs\cite{emacs} users.
Alternate interfaces expand the features of git core to new dimensions.

\textbf{This project aims to build an alternate interface to Git, which can be
  used from JavaScript.}

\section{Why libnodegit?}

\newcommand\sectionTitle[1]{\begin{flushright}\textit{#1}\end{flushright}}
\sectionTitle{The motivations behind the project}

\textit{Git is awesome}! Amazing number of tools have been built using
git, in ways that was never expected. Git at its core is a content
addressable file system which can be used as a database. Its transport
mechanisms are used to deploy applications, synchronize data etc. The
possibilities of git are endless and by providing an alternate
interface to git, libnodegit is extending the possibilities even more.

People have built amazing tools on top of git core, like issue
trackers\cite{gaskit}, blogging engines\cite{octopress}, project
notification systems\cite{git-dude} smarter FTP clients\cite{git-ftp}
that transfer only the changed files, production
quality\cite{gollum-imporoved} wiki\cite{gollum} etc.

Git is the standard way to deploy apps on heroku\cite{git-heroku} now,
one of the largest PaaS\cite{PaaS} providers on the internet. Git is
used in a much simpler manner by designers\cite{git-designers}, with a
smaller subset. A lot of others tools and use cases are listed in the
git wiki\cite{git-tools} for reference.

By providing an API in a very popular, easy to use programming
language, libnodegit aims to help people build the next great tool,
much easier.

\section{Implementation details}

At the heart of the project is a C++ core, written with libgit2 and node.js. The
project core is similar to a \textit{Monolithic kernel}\cite{monolithic_kernel},
where all communication from the JavaScript API, happens through the kernel. Its
not possible for JavaScript API to bypass the core and talk to the git
repository directly like a \textit{Microkernel}\cite{microkernel}

All interactions with git core are done with libgit2. It does the dirty work of
parsing the git object store and returning appropriate data structures back to
the application core. Node.js allows this data to be returned back to the
JavaScript layer, by creating native bindings in C. It is this component that
makes the project possible.

JavaScript executes in various environments now, the most popular ones being web
browsers and \textit{node.js}. It will be possible to write applications that
can harness the power of git core, in a very intuitive manner using libnodegit.
The simple scripts written in JavaScript will be executed by node.js.

\section{Background and recent research}

JavaScript is my primary programming language for last 3 years. I was introduced
to Git over 2 years back and I have worked extensively with it since then. I
spent a 3 month vacation working on a git subsystem called gitweb, trying to
rewrite the all JavaScript in the project in a modern and standards compliant
way, which was a partial success. Love for the tools that is involved and the
confidence that this can be achieved by me on time is the primary motivation
behind choosing this topic
