\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{git} Git version control system.
  \url{http://git-scm.com/}

\bibitem{javascript} Javascript programming language.
  \url{http://en.wikipedia.org/wiki/JavaScript}

\bibitem{magit} It's Magit! An emacs mode for git.
  \url{http://magit.github.com/magit/index.html}

\bibitem{emacs} GNU Emacs, an extensible and customizable text editor.
  \url{http://www.gnu.org/software/emacs/}

\bibitem{twisted} Twisted for python.
  \url{http://twistedmatrix.com/trac/}

\bibitem{eventmachine} EventMachine: Fast, simple event-processing library for
  Ruby programs. \url{http://rubyeventmachine.com/}

\bibitem{npm} Node Package Manager.
  \url{https://npmjs.org/}

\bibitem{node} Node.js, evented IO for Javascript.
  \url{https://nodejs.org/}

\bibitem{gaskit} Gaskit, git backed issue tracker.
  \url{https://github.com/bkeepers/gaskit}

\bibitem{octopress} Octopress, a blogging framework for hackers.
  \url{http://octopress.org/}

\bibitem{git-dude} Git dude, git powered desktop notifier.
  \url{https://github.com/sickill/git-dude}

\bibitem{git-ftp} Git FTP, Git powered FTP client.
  \url{https://github.com/resmo/git-ftp}

\bibitem{gollum-imporoved} Git powered wikis improved.
  \url{https://github.com/blog/774-git-powered-wikis-improved}

\bibitem{gollum} Gollum, git powered wiki.
  \url{https://github.com/gollum/gollum}

\bibitem{git-heroku} Deploying with Git.
  \url{https://devcenter.heroku.com/articles/git}

\bibitem{git-designers} Git for designers.
  \url{http://blog.teamtreehouse.com/git-for-designers-part-1}

\bibitem{git-tools} Git interfaces, frontends, and tools.
  \url{https://git.wiki.kernel.org/index.php/Interfaces,_frontends,_and_tools}

\bibitem{PaaS} Platform as a Service.
  \url{http://en.wikipedia.org/wiki/Platform_as_a_service}

\bibitem{heroku} Heroku, cloud application platform.
  \url{https://www.heroku.com/}

\bibitem{inspiration} Linus Torvalds (2006-05-05). ”Re: [ANNOUNCE] Git wiki”.
  linux-kernel mailing list. ”Some historical background” on git’s predecessors.
  \url{http://marc.info/?l=git\&m=114685143200012}

\bibitem{libgit2} A linkable library for git.
  \url{http://libgit2.github.com/}

\bibitem{libgit2-doc} libgit2 documentation.
  \url{http://libgit2.github.com/libgit2/}

\bibitem{libgit2-api} libgit2 API.
  \url{http://libgit2.github.com/api.html}

\bibitem{github} Github - Social Coding.
  \url{https://github.com}

\bibitem{grit} Object oriented read/write access to Git repositories via Ruby.
  \url{https//github.com/mojombo/grit}

\bibitem{rugged} Ruby bindings for libgit2.
  \url{https://github.com/libgit2/rugged}

\bibitem{luagit2} Lua bindings for libgit2.
  \url{https://github.com/libgit2/luagit2}

\bibitem{pygit2} Python bindings for libgit2.
  \url{https://github.com/libgit2/pygit2}

\bibitem{nodegit} Libgit2 asynchronous native bindings in node.
  \url{https://github.com/tbranyen/}

\end{thebibliography}
