\chapter{Work Done}

The core that is required to build applications is complete and the library is
already usable. It can already read most of the repository properties and
applications can be scripted in JavaScript to work with the log, index etc. The
examples folder in the source contains reference implementations of few standard
git commands, like \texttt{git log --oneline -10}.

The project is very modular, and new features can be added relatively easily
now. Organizing the entire project and getting started were the difficult
challenges.

The magnitude of the project was underestimated while the milestones were
decided, but a good portion of that could be completed on time. The project
required exceptionally good C++ knowledge and required a lot more time than what
was anticipated.

\section{Progress made in previous semester}
\begin{enumerate}
	\item Conducted preliminary research and feasibility study on the subject
	\item Clear project goals were defined
	\item Familiarized with git, learned about the internals and plumbing
    \item Familiarized with libgit2, and its low level C API and how it maps to
      git commands.
    \item Learned extensively about V8 and C++
    \item Designed the JavaScript API
    \item Decided the test suite and wrote initial tests for the API
    \item Got the initial version of the code ready, which could read basic
      repository properties.
    \item Made the design modular so that new features can be added relatively
      easily.
\end{enumerate}

\section{Current status of the project}
\begin{enumerate}
	\item Ability to work with the index
    \item History walking, branching, some visualizations
    \item Read arbitrary commits/blobs/notes/branches
    \item Wrote tests for finished features
    \item Initial work to package the library for simple installation
\end{enumerate}

\section{Milestones which could not be completed}
\begin{enumerate}
	\item File and diff viewing
    \item Read and write repository configurations and settings
    \item Modify history - Write new commits, rebase etc
    \item Network \& initialization features
    \item Asynchronous API
\end{enumerate}
